Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-13 journal/content.tex
Work on discussion

% Defence against criticism for weak evidence in primary studies

* The primary studies were quite openly pro-agile -- how large a factor of bias
  is this?

* Even though most of the primary studies are experience reports and subject to
  bias, this study can draw valuable conclusions. --> If a matter is being
  talked about it must be of some significance.

* The factors that are listed are the ones to discuss -- there may be other
  factors affecting transformation, but this study provides evidence that these
  are the most important ones. We included only challenges that are discussed in
  more than studies, which proves that some filtering has been done.

% Transformation and scaling up

>>>>

% Defence against criticism for weak evidence in primary studies
\subsection{Possible weakness of evidence due to primary study quality}

The strength of evidence of this research may be claimed to be weakened because
of the fact that primary studies were not ranked based on study quality. Primary
studies without proper research methods may bring bias to our results. For
instance, many primary studies were openly pro-agile, without giving a solid
motivation for the standpoint. Although most of the primary studies are
subjective experience reports, we still think this study can draw accurate and
valuable conclusions.

Even if the primary studies do not include rigorous research methods, their
authors have chosen to bring up matters that they consider important. It can be
argued that if a matter is being talked about it must be of some significance.
We believe that the viewpoints on agile transformation that have been elicitated
in this research are the ones to discuss.
In order to strengthen the evidence, we included only viewpoints that are
discussed in several studies.
There may be other factors affecting transformation, but this study provides
evidence that these are the most important ones.

\subsection{Similarity of transformation and scaling up}
